Enter our title here

### 2017-08-14 manuscript.tex
Update manuscript.tex

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
popular interactive teaching technologies have been created including Swirl (need to cite this), LearnR and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback. Swirl is an open source R software package 
that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
curriculum and assign it to students. TryR (Code School 2014) and LearnR are web-based programs and do not have this 
reproducible capability. Public content authoring is not available so educators are limited on what they can teach their 
students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
software than the statistical concepts themselves \citep{Hare2017}.

A not so popular interactive teaching tool is DataCamp- a web application where students can take existing courses or lessons 
that their instructure created.

>>>>

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an open source R software package 
that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
curriculum and assign it to students \citep{Carchedi2014}.

*I'm confused about LearnR and thinks someone else should write about it.*

TryR (Code School 2014) is a web-based programs and do not have this reproducible capability. Since public content authoring is not available, educators are limited on what they can teach their students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

DataCamp is also a web application that offers exhisting interactive R programing courses but unlike TryR, educators can 
create their own courses that coincide with the material.
